An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-21 jmiv.tex
Fix n-neighborhood definition

\begin{definition}[$n$-neighborhood]
\revision{
	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $n$ connected pixels in $R_1(S)$.
}
\end{definition}

@@

Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with \revision{$0 \leq n \leq 50$}.

@@

\begin{figure}
	\center
	\captionsetup{type=table}	
	\revision{
	\begin{tabular}{|c|c|c|}
	\hline
	& Square & Flower \\
	\hline
	$h=1.0$ & 4s & 124s \\
	\hline
	$h=0.5$ & 77s & 1924s\\
	\hline
	$h=0.25$ & 1886s & 28445s\\
	\hline
	\end{tabular}
	}
	\caption{Running times for the local combinatorial optimization algorithm with $0 \leq n \leq 50$. Thirty two threads were used.}
	\label{tab:summary-local-comb-rtime}
\end{figure}

>>>>

\begin{definition}[$n$-neighborhood]
\revision{
	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $k \in [0,n]$ connected pixels in $R_1(S)$.
}
\end{definition}

@@

Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with \revision{$n=50$}.

@@

\begin{figure}
	\center
	\captionsetup{type=table}	
	\revision{
	\begin{tabular}{|c|c|c|}
	\hline
	& Square & Flower \\
	\hline
	$h=1.0$ & 4s & 124s \\
	\hline
	$h=0.5$ & 77s & 1924s\\
	\hline
	$h=0.25$ & 1886s & 28445s\\
	\hline
	\end{tabular}
	}
	\caption{Running times for the local combinatorial optimization algorithm with $n=50$. Thirty two threads were used.}
	\label{tab:summary-local-comb-rtime}
\end{figure}
